\documentclass[letterpaper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=0.85in}
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=*}

\begin{document}

\begin{center}
    {\Large \textbf{Fernando Rodríguez Prianti}}\\[0.1cm]
    {\large Software Engineer · Full Stack}\\[0.15cm]
    Xalapa, Veracruz, Mexico \\
    \href{mailto:fernando.rdz.prianti@gmail.com}{fernando.rdz.prianti@gmail.com} \quad | \quad +52 228 537 2622 \\
    \href{https://www.linkedin.com/in/fernando-rodr{\'i}guez-732670140/}{LinkedIn} \quad | \quad
    \href{https://github.com/FernandoRP-nan}{GitHub} \quad | \quad
    \href{https://fernandorp-nan.github.io/fernando-cv/}{Web CV}
\end{center}

\section*{Profile}
Software Engineer with 3+ years in web and mobile. Production PWAs and portals (Angular, Laravel), Android with Jetpack Compose, and multi-repo ecosystems. Experience with Stripe, JWT/RBAC, FCM push, WebSockets, and Docker. Side projects: Python, Godot, Obsidian plugins, and local RAG (LangGraph + Ollama).

\section*{Experience}
\textbf{Tierra de Perros} \hfill \textit{DEC 2024 -- DEC 2025 · 13 months}\\
Xalapa, Veracruz
\begin{itemize}
    \item Angular + Laravel PWA: appointments, store, Stripe, WebSocket chat, roles.
    \item FCM push, JWT. Platform still live; contract ended Dec 2025.
\end{itemize}

\textbf{Bachilleres Veracruz Portal} \hfill \textit{SEP 2024 -- DEC 2024 · 4 months}\\
Xalapa, Veracruz
\begin{itemize}
    \item Government portal with PHP + JS: news, schedules, notices, JWT roles.
\end{itemize}

\textbf{Satori Tech -- Jr. Android Developer} \hfill \textit{SEP 2021 -- JUN 2024 · 33 months}\\
Mecatepec, CDMX
\begin{itemize}
    \item Kotlin apps with MVVM, Retrofit, Room, and agile methodology.
\end{itemize}

\textbf{Grupo Modelo -- SAP PI PO Jr. Consultant (Freelance)} \hfill \textit{JUN -- AUG 2022 · 3 months · concurrent with Satori}\\
Xalapa, Veracruz
\begin{itemize}
    \item SAP ERP support while continuing at Satori Tech.
\end{itemize}

\section*{Featured projects}
\textbf{Pokédex} (2024 · 4 months): Kotlin, Compose, Room, Retrofit, MVVM.\\
\textbf{Uno Bank} (2026): Compose, Clean Architecture, Paging, Hilt, biometrics, simulated backend.\\
\textbf{Cero — Movies \& Compose} (2026): Compose, Hilt, Room, Retrofit, TMDB, NDK module.\\
\textbf{Point of Sale} (2024): Node.js, React, MySQL, JWT, manager/cashier roles.\\
\textbf{Gallery AYN} (2024): Python, Svelte desktop gallery and video tools.\\
\textbf{All You Need} (2022--2025): Android Compose + Spring Boot + CouchDB ecosystem.\\
\textbf{DFS Path Finder} (2024): Python 8-puzzle with DFS and state validation.\\
\textbf{Vault Plugins} (2024--2025): TypeScript, Obsidian API (tasks, collection, agenda).\\
\textbf{AI Obsidian Manager} (2025): LangGraph, Ollama, ChromaDB, Docker.

\section*{Technical stack}
\textbf{Languages:} Java, Kotlin, Python, JavaScript, TypeScript, PHP, GDScript, C++.\\
\textbf{Frameworks:} Angular, Laravel, React, Node.js, Express, Spring Boot, Svelte, Godot, PWA.\\
\textbf{Android:} Jetpack Compose, Hilt, Room, Retrofit, Paging, Coil, NDK, Biometric.\\
\textbf{Databases:} MySQL, SQLite, CouchDB.\\
\textbf{Integrations:} Stripe, Firebase FCM, WebSockets, REST API, JWT, Obsidian API, SAP ERP.\\
\textbf{Tools:} Git, GitHub Actions, Docker, Android Studio, VS Code, Gradle, Vite.\\
\textbf{Practices:} MVVM, Clean Architecture, Repository, dependency injection, RBAC, offline-first paging.\\
\textbf{AI:} LangGraph, Ollama, ChromaDB, RAG.

\section*{Education}
\textbf{Bachelor's in Computer Systems Engineering -- Software Specialization}\\
Instituto Tecnológico Superior de Xalapa \hfill 2019 -- 2025

\section*{Languages}
Spanish (native) · English (A2)

\end{document}
